\documentclass[11pt]{article}

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{etoolbox}
\hypersetup{hidelinks}
\usepackage[a4paper,
            %bindingoffset=0.2in,
            hmargin=0.5in,
            vmargin=0.5in,
            marginparwidth=0pt]{geometry}
\pagestyle{empty}

%Custom parameters
\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}
\newlength{\seperate}
\setlength{\seperate}{2px}

%Formatting default parameters
\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
%\setlength{\tabcolsep}{0in}

%Colours here
\definecolor{contactgrey}{rgb}{0.33, 0.33, 0.33}
\definecolor{darkblue}{rgb}{0,0,0.5}
%\definecolor{}

\title{CV}
\author{Meshwil}
\date{\today}

%Commands here
%\renewcommand{\hrulefill}{\leavevmode\leaders\hrule height 2pt\hfill\kern\z@}
\newcommand{\coloredhrulefill}[2][black]{%
    \leavevmode%
    \leaders\hbox{\textcolor{#1}{\rule{1ex}{0.5pt}}}\hfill\kern0pt%
}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\end{center}}
\newcommand{\location}[1]{\begin{center}#1\end{center}}
\newcommand{\contactSpace}{\hspace{0.25cm}.\hspace{0.25cm}} % Missing closing curly bracket
\newcommand{\contact}[1]{\vspace*{2\secsep}\begin{center}\small#1 \end{center}\vspace*{2\secsep}} % Added missing [1]
\newcommand{\lineunder}{\vspace*{-24pt} \hspace*{-6pt} \coloredhrulefill[contactgrey]{}  \\* \vspace*{-15pt}}


%Environments here
\newenvironment{resume_header}{}{\vspace{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newenvironment{tabbedList}[1]{
	\begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{10pt}
      \setlength{\rightmargin}{0pt}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
	}
	\item[]
}{\end{list}}

\newenvironment{notabbedList}{
	\begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newenvironment{resume_section}[1] {
	%\filbreak
	%\vspace{1\secsep}
	\textsc{\Large #1} \\*
	
	\lineunder
	\begin{tabbedList}{\secsep}
}{\end{tabbedList}\vspace{1.2\secsep}}

\newenvironment{resume_subsection}[4] {
	\textbf{#1} \hfill {\footnotesize #2}\vspace*{-1px}\\*  %\hspace{2em}
	{\small#3} \hfill {\footnotesize \textit{#4}} \hspace{-4px}\vspace*{-8px}
	
	\begin{tabbedList}{0pt}
}{\end{tabbedList}}

\newenvironment{personal_projects}[4] {
	\textbf{#1} \href{#4}{#3} $\mid$ {\scriptsize #2}  %\hspace{2em}
	\vspace*{4px}
	\begin{tabbedList}{0pt}
}{\end{tabbedList}\vspace*{1.5\secsep}}

\newenvironment{subitems}{
	\vspace*{-2px}
	%\renewcommand{\labelitemi}{\color{contactgrey}{\faCode}}
	\begin{itemize}[left=2pt]
		\setlength{\labelsep}{0.3em}
		\setlength{\itemsep}{0pt}
		\setlength{\parsep}{0pt}
		\setlength{\topsep}{0px}
}{\end{itemize}}

%begins here

\begin{document}
	\begin{resume_header}
		\name{Meshwil Dias}
		\contact{\faPhoneSquare \hspace{\secsep} 07865076487 \contactSpace \href{mailto:meshwildias@gmail.com}{\faSend \hspace{\secsep}meshwildias@gmail.com } \contactSpace \href{https://www.meshwildias.site/}{\faCompass \hspace{\secsep}meshwildias.site} \contactSpace \href{https://github.com/02MESH}{\faGithub \hspace{\secsep}02MESH} \contactSpace \href{https://www.linkedin.com/in/mad-0000/}{\faLinkedinSquare \hspace{\secsep}Meshwil Dias}}
	\end{resume_header}
	
	\vspace*{1.5\seperate}	
	
	%Education
	\begin{resume_section}{Education}
    \begin{resume_subsection}{University of Kent}{Canterbury, Kent}{\textbf{First Class Honours} in BSc Computer Science }{Sep 2021 - July 2024}
		\end{resume_subsection}
		
		%\vspace*{\seperate}
		
		\begin{resume_subsection}{St. Gregory's Catholic Science College}{Harrow, Greater London}{A-Levels in Business Studies\textit{(B)}, Computer Science\textit{(B)} \& Psychology\textit{(B)}}{Sep 2018 - Apr 2021}
		\end{resume_subsection}
	\end{resume_section}
	
	\begin{resume_section}{Personal Projects}
	
		%%%%%%%%%%%%%%%%%%%%%%%%%%
		\begin{personal_projects} {Passlock}{Typescript, React, Node, Electron, CSS, Docker, MySQL, Prisma}{\faGitlab}{https://github.com/02MESH/docker-container-hosting}
			\begin{subitems}
				\item{Developing a team-oriented full-stack \textbf{password managing web application} that involves using an encrypted \textbf{REST API}, with \textbf{React} handling the frontend presented as an app through \textbf{Electron}.}
				\item{Implemented the back-end using \textbf{Docker} along with \textbf{MySQL} and \textbf{Prisma} containers running on a custom port that serves data to the Frontend.}
				\item{Master(i.e. Client) passwords are hashed using the \textbf{SHA256} hashing algorithm along with \textbf{AES256} encryption/decryption for saving/displaying the users' passwords. This is established in the front-end.}
				\item{Testing methods such as \textbf{unit}, \textbf{acceptance} \& \textbf{integration} tests were used.}
			\end{subitems}
		\end{personal_projects}	
	
		\vspace*{\seperate}
		
		\begin{personal_projects}{AirAware}{C/C++, Arduino, HTML/CSS, Firebase, Twilio, ChartJS, JavaScript}{\faGithub}{https://github.com/02MESH/AirAware}
			\begin{subitems}
				\item{Developed a air-monitoring system which used a PM2.5 (Dust) \& DHT11 (Humidity \& Temperature) sensors that informed users through the \textbf{Twilio} client through SMS whenever user-set thresholds were breached.}
				\item{Utilised the \textbf{Firebase realtime} database which fed live data to the webpage that updated itself in \textbf{15} second intervals for accurate telemetry.}
				\item{Implemented the sensor data GUI through \textbf{ChartJS}.}
			\end{subitems}
		\end{personal_projects}
			
		\vspace*{\seperate}			
			
		%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\begin{personal_projects} {Shopping Website}{HTML \& CSS, JS (NodeJS) \& Express, EJS, MongoDB \& Mongoose}{\faGithub}{https://www.google.com/}
			\begin{subitems}
				\item{Built a robust and scalable website by using \textbf{Express} for routing, middleware management, and handling \textbf{HTTP requests}.}
				\item{Implemented server-side logic using \textbf{Node} to manage product listings, user authentication, shopping cart functionality, order processing and database interactions.}
				\item{Used the \textbf{Mongo} DBMS which was served using a ODM tool i.e. \textbf{Mongoose}.}
				\end{subitems}
			\end{personal_projects}
		
		\vspace*{\seperate}	
		
		%Completed Project
		\begin{personal_projects} {Hospital Management System}{Java, MySQL}{\faGitlab}{https://git.cs.kent.ac.uk/taa40/software-development}
			\begin{subitems}
				\item{Collaborated in a 4 member team to engineer bespoke software for Doctor-Receptionist co-ordination using the \textbf{SCRUMS} management approach.}
				\item{Designed the \textbf{MySQL DBMS} which ran on a \textbf{Linux} server.}
				\item{Extensive focus on \textbf{regression} and \textbf{integration} testing using \textbf{JUnit}.}
				\item{Regular \textbf{sprints}, retrospectives, \& task estimation.}
			\end{subitems}
		\end{personal_projects}		
		
		%Completed Project
		\begin{personal_projects} {Custom Language Compiler}{C++, Bash}{\faGithub}{https://github.com/02MESH/DOPL-Compiler}
			\begin{subitems}
				\item{Engineered a \textbf{tokeniser-parser} to identify diverse datatypes and assess syntax validity of a language known as DOPL.}
				\item{Designed an \textbf{O(n)} time-complexity \textbf{lexical analysis} algorithm and created a comprehensive testing suite with \textbf{10+ meticulous tests} for precise compilation validation triggered by a simple \textbf{bash} script.}
			\end{subitems}
		\end{personal_projects}
		
		\vspace*{\seperate}	
	
		%Completed Project
		\begin{personal_projects} {Chess}{Python, PyGame}{\faGithub}{https://github.com/02MESH/Chess}
			\begin{subitems}
				\item{Implemented using the \textbf{PyGame} library to research AI algorithms i.e. \textbf{Minimax}.}
				\item{Game modes included single-player (computer) \& multiplayer (play with friends).}
				\item{Designed the game using the \textbf{OOP} design which used a modular structure.}
			\end{subitems}
		\end{personal_projects}
		
	\end{resume_section}
		\begin{resume_section}{Technical Skills}
		\begin{notabbedList}
			\textbf{Languages \& DBs} \hspace*{5pt} \= C++, Python, Java, Javascript, HTML/CSS, MySQL, MongoDB \\*
			\textbf{Frameworks} \> Node, React, Bootstrap,  Express, Sequelise, Mongoose\\*
			\textbf{Other Technologies} \> Docker, CI \& CD Pipelines (GitHub Actions), \LaTeX, Neovim\\*
		\end{notabbedList}
	\end{resume_section}
\end{document}
